<<<<<<< HEAD
---
title: "QRM II Graded Assignment (13)"
subtitle: "Period 1, 2026"
author: "Fill in your group number and names here"
date:  "`r format(Sys.Date(), '%d-%m-%Y')`"
output:
  pdf_document:
    number_sections: true
  html_document:
    df_print: paged

header-includes:
- "\\setcounter{section}{-1}"
- |
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{
    showspaces = false,
    showtabs = false,
    breaklines,
    commandchars=\\\{\}
format:
  html:
    code-overflow: wrap
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This assignment is to be completed in groups of 4-5. Further, all
students in your group need to be assigned to the same R tutorial group
(Friday's tutorial). You can sign yourself up for a group on Canvas.
Please do so
\textbf{before the start of your first R tutorial on Friday September 4th.}
You can use the Discussion Board in Canvas if you do not have a group
yet or if your group is incomplete.

The assignment has 5 parts, and each part corresponds to the course
material of that week (with the exclusion of week 6, for which there is
no R programming material).

You are supposed to hand in these assignments on Canvas at the following
dates:

- **Deadline 1** *Sunday September 27th, at 23:59pm*: you are supposed
  to hand in weeks 1, 2, and 3 of this assignment. This will determine
  18% of your overall course grade
- **Deadline 2** *Sunday October 11th, at 23:59pm*: you are supposed to
  hand in weeks 4, and 5 of this assignment. This will determine 12% of
  your overall course grade

The R tutorials (each Friday) will consist of two halves. During the
first half, you will discuss the tutorial exercises. These can be
downloaded separately from Canvas. During the second half, you can work
on this graded assignment within your own group. The purpose is that you
find out how to work with R for doing statistical analyses by yourself.
The tutorial exercises are meant to teach you basic commands to get you
started, but to answer the problem sets in this assignment, you might
need to research your own solutions, and use functions and commands not
described in the tutorial exercises. Learning how to solve your own
research problems is integral part of learning R. When you and your
group get stuck on how to approach an exercise, the hierarchy in finding
your way is as follows:

- use the concepts from the tutorial exercises;
- use the cheat sheets available on Canvas;
- use Google, YouTube, StackOverflow, or another website;
- ask the teacher.

The use of generative AI is \textbf{not} permitted and may result in a
grade of 0. See the AI protocol in the course manual for details.

To answer the assignment, you can simply fill out this R markdown
document. There are designated places which you can fill with R code.
There are also designated spaces for you to answer each question. Often,
the structure of an answer will be as follows. First, you type the R
code in the designated box. This will show how you analyzed the data to
get the answer to the question. Below the box for the R code, you will
then summarize your answer to the question, i.e. what are the
conclusions that you draw from the data analysis?

When handing in, you are supposed to submit this .Rmd file, and a
knitted version of this document. You can knit this document to pdf,
word, or html. Knitting to pdf requires you to have a .tex distribution
installed on your computer. Knitting to Word requires you to have Word
installed.

The exercises are designed such that you should be able to finish the
majority of them during the tutorial each week. If you are not able to
finish them fully during that time, you are expected to work on it in
your own time using the computers on campus or your own device. It is
best to meet as a group in-person when working together. If you want to
work remotely, github is a good platform to guarantee smooth
collaboration. Alternatively, you can email this .Rmd file back and
forth to one another as a group, but this is not recommended as it is
more cumbersome.

We encourage you to keep your code blocks, printing statements, and
final answers, as short as possible. In any case, there is a page limit
of 6 pages per week, which encompasses the total length of this document
which consists of the questions, your coding lines, and your answers.
When your answers to questions of the respective week exceed this page
limit, they will not be graded, resulting in zero points.

Each week consists of 1, 2, or 3 subquestions. The total amount of
points you can earn per week is 20 points.

# Week 1

1.  Find the dataset “movies1.tsv” on Canvas. Describe your data set:
    How many observations does it have. How many variables are there?
    How many subjects? What consists of a subject? \textbf{[4 points]}

```{r}
install.packages("readr")
```

```{r}
library(readr)
```

```{r}
movies1 <- read_tsv("movies1.tsv")
```

```{r}
#observations
NROW(movies1)*NCOL(movies1)
#variables
NROW(movies1)
#subjects
NCOL(movies1)

```

all data acquired from a singular entry/instance during the study is
what consists of a subject

Write your response here.

2.  Which of the following types of variables are present in your data
    set? (i) nominal; (ii) ordinal; (iii); interval; (iv) ratio. If
    present, name one example of such a variable present in your data
    set. \textbf{[4 points]}

```{r}
names(movies1)
```

**nominal** present, an example of this is the "title" variable

**ordinal** present, an example of this is the "vote_average" variable

**interval** present, an example of this is the "release_date" variable

**ratio** present, an example of this is the "budget" variable\`

3.  A movie studio wants to know which types of movies are best at
    generating profit. The measure they use for this is the
    profitability ratio, which is defined as
    $$PR=\frac{Revenue}{Budget}.$$ Perform the following steps to
    provide the movie studio with an analysis which corresponds to their
    request:

<!-- -->

a.  Create the variable PR as the revenue of a movie divided by its
    budget. Report its mean, median, maximum, and minimum.
    \textbf{[2 points]}
b.  As you can probably see from your answer in a.), some movies have a
    PR of "Inf". What does this mean? Why are some movies assigned this
    value? \textbf{[2 points]}
c.  As you can probably see from your answer in a.), some movies have a
    PR of "NA". What does this mean? Why are some movies assigned this
    value? \textbf{[2 points]}
d.  For the movies that have a PR of "Inf", set its PR to "NA". After
    doing this, report the mean, median, maximum, and minimum of PR. How
    do you interpret the mean? \textbf{[2 points]}
e.  What does a PR of at least one mean? What is the fraction of movies
    that have a PR of at least one? \textbf{[2 points]}
f.  Create a boxplot of the variable PR. Make sure it has an appropriate
    title, and appropriate titles and labels for the x- and y-axis.
    Describe the shape of the boxplot. Give $Q_1$, $Q_2$, $Q_3$ and
    $Q_4$. What does this tell you about the nature of making money in
    the movies industry? \textbf{[2 points]}

For each step, you should provide first all the code you used to answer
the question and then formulate an answer using full sentences.

*Step a*

```{r}
movies1$PR <- movies1$revenue / movies1$budget
summary(movies1$PR)

```

**Your Answer:**

mean = infinite median = 2.0409 minimum = 0.0000 maximum = infinite

*Step b*

```{r}
is.infinite(movies1$PR)
```

**Your Answer:**

the reason why some results show a PR of infinite is because they made a
revenue with a budget of \$0.

*Step c*

```{r}

is.na(movies1$PR)

```

**Your Answer:**

the reason why PR is sometimes NA is because the movie didn't make any
revenue, causing the code to divide by 0.

*Step d*

```{r}
movies1$PR[is.infinite(movies1$PR)] <- NA

summary(movies1$PR)

```

**Your Answer:**

the mean here can be interpreted as the mean excluding any results where
PR was either infinite or NA.

*Step e*

```{r}
movies1$PR[is.na(movies1$PR)] <- 0 #to exclude from being greater than 1
countPR1 <- 0
for (PR in movies1) {
  countPR1 <- countPR1 + 1
} 
PR_fraction <- countPR1 / nrow(movies1)
  print(PR_fraction)

```

**Your Answer:**

using the code, we can determine that 3,96% of the dataset results in an
NA.

*Step f*

```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)

boxplot(movies1$PR,
        main = "Boxplot of Profitability Ratio (PR)",
        xlab = "Movies",
        ylab = "Profitability Ratio (PR)")

quantile(movies1$PR, probs = c(0.25, 0.50, 0.75, 1), na.rm = TRUE)

```

**Your Answer:** q_1 = 0.6239106 q_2 = 1.9412588 q_3 = 3.6700769 q_4 =
426.6441000

there are 2 main observations that can be made from looking at these
numbers. first off, the second quarter being greater than 1 shows that
at least 50% of movies earn more revenue than they have to spend on
their budget. secondly, the result of the 4th quarter is a lot higher
than the other results. by looking at the boxplot we can see that this
is the result of an outlier.

# Week 2

1 Is your dataset movies1.tsv the full population, or is it a sample of
a larger population? If the latter, how would you describe the full
population? \textbf{[4 points]}

**Your Answer**

the dataset movies1.tsv is not the full population, but rather a sample
of a larger population. this full population can be described as all
movies ever made, of which the dataset is only a small sample (505).

2 Let M be the event that a movie director is male. Let R be the runtime
of the movie.

a.  Using your data, calculate $P(M)$. What is $P(M')$?. Calculate
    $P(M')$ as well. \textbf{[1 point]}
b.  Assume R is normally distributed with $\mu=107$ and $\sigma=22$,
    calculate $P(90 \leq R \leq 120)$. \textbf{[1 point]}
c.  Calculate $P(90 \leq R \leq 120)$ empirically using your data. How
    accurate were the assumptions about the distribution of R in 2b?
    Which of the assumptions do you consider the most suspect? Explain.
    \textbf{[2 points]}
d.  Using your data, calculate $P(120 \leq R | M')$ \textbf{[2 points]}

*step a*

```{r}
names(movies1)
table(movies1$director_gender)

P_M <- mean(movies1$director_gender == "male", na.rm = TRUE)
P_M

P_not_M <- 1 - P_M
P_not_M

```

**Your Answer:**

The probability that a movie has a male director (P(M)) is approximately 90.64% meaning that the probability that a movie does not have a male director (P(M')) is then 9.36%.


*step b*

```{r}
pnorm(120, mean = 107, sd = 22) -
  pnorm(90, mean = 107, sd = 22)

```

**Your Answer:**

When we assume the mean runtime is 107 minutes with a standard deviation of 22 minutes the probability that a movie has a runtime between 90 and 120 minutes is approximately 50.3%.

*step c*

```{r}
P_runtime <- mean(movies1$runtime >= 90 & movies1$runtime <= 120,
                  na.rm = TRUE)
P_runtime
mean(movies1$runtime, na.rm = TRUE)
sd(movies1$runtime, na.rm = TRUE)

hist(movies1$runtime,
     main = "Distribution of Movie Runtime",
     xlab = "Runtime (minutes)")

mean(movies1$runtime, na.rm = TRUE)
sd(movies1$runtime, na.rm = TRUE)
```

**Your Answer:**

The empirical probability that a movie has a runtime between 90 and 120 minutes is 62.3% which is higher than the previously theoretical probability of 50.3% calculated in 2b. In 2b we assumed that the mean is 107 and the standard deviation is 22. This is actually very close to the actual mean and the actual standard deviation which are 106.95 minutes for the mean and 21.98 minutes for the standard deviation. Therefore, the assumption that causes the difference in results is mostl likely that we assumed that runtime is perfectly normal distributed while this is not true. Shown by the histogram we can see that runtime actually has a long right tail.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

3 For this question, you will again use the profitability ratio PR. Make
sure that PR is defined the same way as in question 3d of week 1. For
this question, you will assume that your data set is the full
population.

a.  What is the mean of the variable PR in your data set?
    \textbf{[2 points]}
b.  Create a new data set, called movies_sample. Make sure that it is a
    random sample of your data set of 25 movies. What is the mean of PR
    in this random sample? How does it compare to the mean of PR in 3a?
    \textbf{[2 points]}
c.  In a for loop, create 100 different samples of 25 movies, as in b,
    and estimate the mean within each sample. Save the mean of each
    sample in a vector called sample_means. So the first position of the
    vector would have the mean of the first sample, the second position
    the mean of the second sample, etc. Print this vector.
    \textbf{[2 points]}
d.  Summarize and make a histogram of sample_means. What is the mean,
    standard deviation and shape of its distribution?
    \textbf{[2 points]}
e.  Using the formulas of the *Central Limit Theorem*, give the
    distribution of the sample mean of PR in a sample of 25 movies from
    you population (including its expected value and standard
    deviation). How do these values compare to your answers at d.)?
    \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

**Your Answer:**

Write your formulated response here.

# Week 3

1.  For the next part of the assignment, assume that the movies in your
    data frame are a random sample of a larger population of movies.

<!-- -->

a.  Create a new data set that only includes movies that are of the
    genre "Thriller". For these thriller movies, give a 99 percent
    confidence interval for the variable *vote_average*.
    \textbf{[2 points]}

b.  According to IMDB, the average movie is rated with a 6.5. Using your
    data, test for the null hypothesis that thriller movies are at least
    as good as the average movie, against the alternative hypothesis
    that thriller movies are rated worse than the average movie. Test
    this hypothesis using an approporiate five-step procedure. What is
    your p-value and what do you conclude? \textbf{[2 points]}

*step a*

```{r}
movies1 <- read.delim("movies1.tsv")

thriller <- subset(movies, genre == "Thriller")

t.test(thriller$vote_average, conf.level = 0.99)

```

**Your Answer:**

we are 99% confident that the true mean vote average of thriller movies
in the population lies between [5.644845, 6.299771] *step b*

```{r}
#WRITE YOUR CODE HERE
t.test(thriller$vote_average,
       mu = 6.5,
       alternative = "less")

```

**Your Answer:**

five step procedure 1. hypothesis H₀: μ ≥ 6.5 the average rating of
thriller movies is at least 6.5

H₁: μ \< 6.5 the average rating of thriller movies is lower than 6.5

2.  significance level we use α = 0.05

3.  test statistic you can see the code above. with t = -4.2782 and df =
    64

4.  determine the p-value p-value = 0.0000321 0.0000321 \< 0,05, we
    reject H₀

5.  conclusion we reject the null hypothesis and conclude that there is
    sufficient evedence to state that the average rating of thriller
    movies is lower than a 6.5. the mean is given by point 3 and shows a
    mean of 5.9723, which is also below 6.5

2

a.  How many movies in your sample had a female lead actor? How many had
    a male lead actor? \textbf{[2 points]}
b.  Test the null hypothesis that for any given movie the chance that
    the lead actor is male or female is equal. Clearly state your null
    hypothesis and alternative hypothesis, and your chosen significance
    level. Use an appropriate R function to test your hypothesis, and
    state your conclusion. Also give the p-value that corresponds to
    your test statistic. \textbf{[2 points]}
c.  What is the variance of the profitability ratio (PR) for movies with
    a male lead actor? What is the variance of profitability ratio for
    movies with a female lead actor? Make sure that PR is defined in the
    same way as in week 1. \textbf{[2 points]}
d.  Assume that the variance of PR for movies with a male lead actor in
    your data is the same as the variance for movies with a male lead
    actor in your population (that is, there is no sampling uncertainty
    in this estimate). Now, set up a hypothesis test to test for the
    null hypothesis that the PR for movies with a female lead is equal
    to the variance for movies with a male lead actor. Clearly state
    your null hypothesis and alternative hypothesis, and your chosen
    significance level. Calculate your test statistic and tell how your
    test statistic is distributed, and state your conclusion. Also give
    the p-value that corresponds to your test statistic.
    \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
table(movies1$first_actor_gender)

```

**Your Answer:**

There are 130 female lead actors and 352 male lead actors

*step b*

```{r}
binom.test(
  sum(movies1$first_actor_gender == "male", na.rm = TRUE),
  sum(!is.na(movies1$first_actor_gender)),
  p = 0.5
)

```

**Your Answer:**

1.  hypothesis H₀:pmale=pfemale=0.5 The probability of a male lead actor
    equals the probability of a female lead actor H₁:pmale ≠ pfemale it
    is not equal to eachother

2.  significance level we use α = 0.05

3.  R function see the code above

There were 352 male first actors out of 482 movies, giving a sample
proportion of 73.03%. The p-value is 2.2 × 10⁻¹⁶, which is smaller than
0.05.

Therefore, we can reject the null hypothesis. There is significant
evidence that the probability of a male first actor is different from
50%. In this sample, the proportion of male first actors is
approximately 73%.

*step c*

```{r}
male <- subset(movies1, first_actor_gender == "male")
female <- subset(movies1, first_actor_gender == "female")
var(male$PR, na.rm = TRUE)
var(female$PR, na.rm = TRUE)

```

**Your Answer:**

variance of PR for movies with a male lead: 77.73981 Variance of PR for
movies with a female lead: 1398.035

*step d*

```{r}
n_female <- sum(!is.na(female$PR))
test_stat <- (n_female - 1) * var_female / var_male

test_stat

df <- n_female - 1

p_value <- 2 * min(
  pchisq(test_stat, df = df),
  1 - pchisq(test_stat, df = df)
)

p_value

```

**Your Answer:**

1.  hypothesis H₀:σ\^2 male= σ\^2 female=0.5 The variance of PR for
    female lead movies equals the variance for male lead movies of a
    female lead actor H₁:σ\^2 male ≠ σ\^2 female the variance is
    different

2.  significance level we use α = 0.05

3.  R function see the code above because the male variance is known, we
    use a chi-squared test

4.  p-value see the code above. The P-value is 0

5.  conclusion The p-value is \<0.05, this means we reject H₀ and the is
    sufficient evidence to conclude that the variance of the probability
    ratio for movies with a female lead actor differs from the movie
    with male lead actors

3

a.  Create a new variable called genre2. Make sure that the three most
    popular genres remain the same, but that all the other genres get
    categorized into one genre called "Other". Report a frequency table
    of this new variable genre2. \textbf{[2 points]}
b.  Create a scatter plot with each type of genre2 on the x axis and the
    mean of PR within that genre on the y-axis. Make sure it has an
    appropriate title, and appropriate titles and labels for the x- and
    y-axis. Which movie genre has the highest PR? Which has the lowest?
    \textbf{[2 points]}
c.  Recreate the scatter plot, but now add bars around each point,
    indicating the 95% confidence interval. \textbf{[2 points]}
d.  Now, create a new data frame which is a random subsample of n=100 of
    your full data frame. Recreate the plot in c.) How do the confidence
    intervals compare to the confidence intervals you plotted in c.)?
    \textbf{[2 points]}

*step a*

```{r}
table(movies1$genre)


movies1$genre2 <- ifelse(movies1$genre %in% c("Drama", "Comedy", "Thriller"),
                         movies1$genre, "Other")

table(movies1$genre2, useNA = "no")

```

**Your Answer:**

The three most popular genres are Drama, comedy and thriller

*step b*

```{r}
aggregate(PR ~ genre2, data = movies1, mean, na.rm = TRUE)

genre_means <- aggregate(PR ~ genre2, data = movies1, mean, na.rm = TRUE)

plot(as.factor(genre_means$genre2),
     genre_means$PR,
     main = "Mean PR by Movie Genre",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

```

**Your Answer:**

the movie genre with the highest PR are the thriller movies with a PR of
8.921 and the movie genre with the lowest PR are the Drama movies with a
PR of 1.997

*step c*

```{r}
genres <- unique(na.omit(movies1$genre2))

means <- numeric(length(genres))
lower <- numeric(length(genres))
upper <- numeric(length(genres))

for (i in 1:length(genres)) {
  x <- movies1$PR[movies1$genre2 == genres[i]]
  x <- x[!is.na(x)]
  
  test <- t.test(x)
  
  means[i] <- mean(x)
  lower[i] <- test$conf.int[1]
  upper[i] <- test$conf.int[2]
}

x <- 1:length(genres)

plot(x, means,
     xaxt = "n",
     main = "Mean PR by Movie Genre with 95% Confidence Intervals",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

axis(1, at = x, labels = genres)

arrows(x, lower,
       x, upper,
       angle = 90,
       code = 3,
       length = 0.05)


```

**Your Answer:**

see the code above

*step d*

```{r}
set.seed(123)

movies_sample <- movies1[sample(nrow(movies1), 100), ]
genres <- unique(na.omit(movies_sample$genre2))

means <- numeric(length(genres))
lower <- numeric(length(genres))
upper <- numeric(length(genres))

for (i in 1:length(genres)) {
  x <- movies_sample$PR[movies_sample$genre2 == genres[i]]
  x <- x[!is.na(x)]
  
  test <- t.test(x)
  
  means[i] <- mean(x)
  lower[i] <- test$conf.int[1]
  upper[i] <- test$conf.int[2]
}

x <- 1:length(genres)

plot(x, means,
     xaxt = "n",
     main = "Mean PR by Movie Genre (Sample of 100)",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

axis(1, at = x, labels = genres)

arrows(x, lower,
       x, upper,
       angle = 90,
       code = 3,
       length = 0.05)
```

**Your Answer:**

the confidence intervals are generally wider for the random sample of
100 observations. this is because the smaller sample size results in a
larger standard error and therefore uncertainty around the estimated
mean

# Week 4

1.  There is an argument going on in the movie studio. *Bob* claims that
    production budgets are getting out of hand, and that the studio
    should focus on making cheaper movies. *Chantal* disagrees. She
    tells Bob that \`\`The profitability ratio of the movie will remain
    similar, no matter how much the budget is''.

<!-- -->

a.  Set up a regression model to test Chantal's claim, and estimate it.
    That is, estimate:
    $$\text{PR}_i=\beta_0+\beta_1 \text{Budget}_i +\varepsilon_i.$$
    Print a summary of your estimated model. \textbf{[2 points]}
b.  What is the estimated value of $\beta_1$ how do you interpet it?
    \textbf{[2 points]}
c.  Test for the null hypothesis that $\beta_1 = 0$. Report the p-value
    and state your conclusion. \textbf{[2 points]}
d.  Who do you think is correct? Bob or Chantal? What would you advise
    the movie studio to do? \textbf{[2 points]}
e.  Make a histogram of the residuals of your model. Based on the
    histogram, do you have any reason to doubt the validity of your
    model? Explain. \textbf{[2 points]}
f.  Estimate hatvalues for each observation that you used to estimate
    your model. Do any hatvalues exceed the critical value? Based on
    this analysis, do you hvae any reason to doubt the validity of your
    model? \textbf{[2 points]}
g.  Based on your analysis in f.), estimate your model again, but remove
    any outliers. Print a summary of your model and again test for the
    null hypothesis that $\beta_1 = 0$. What do you conclude? Based on
    this new model, would your advice to the movie studio in question d.
    change? \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step f*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step g*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

2.  

<!-- -->

a.  Make a scatterplot with vote_average on the y-axis, and runtime on
    the x-axis. Within the same scatterplot, draw a straight line which
    summarizes the association between the average vote and the runtime.
    \textbf{[3 points]}
b.  Using the insights from the scatterplot, your linear model, and your
    data, find an example of a movie that vastly overperformed. That
    means, find a movie that had much higher average vote than expected,
    given its runtime. For this movie, report its vote_average, its
    predicted vote_average, and its residual. \textbf{[3 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

# Week 5

a.  Create a plot of the mean PR by year of release. Include 95%
    confidence intervals around each mean Do you see any indication of a
    time trend in the PR? \textbf{[4 points]}
b.  Estimate an OLS model which has as dependent variable the PR of a
    movie, and as independent variable the log of budget, a dummy for
    each level that genre2 can take, and the year of release. Show a
    summary of the resulting model and interpret each coefficient.
    \textbf{[4 points]}

The movie studio that you work is releasing a new movie in May of 2026.
It will be a Comedy movie with a budget of 40,000,0000. It will have a
runtime of 160 minutes.

c.  Estimate a model that is able to predict the revenue of this movie.
    Give its predicted revenue and include a 95% prediction interval.
    \textbf{[6 points]}
d.  Plot the residuals against various independent variables in the
    model. Do you find any evidence of heteroskedasticity?
    \textbf{[2 points]}
e.  The movie is set in Germany. The director wants to make the movie
    with only german-speaking actors. The executive producer is strongly
    against this, as she is afraid that movies that are not english
    spoken will have a low profit ratio. Estimate a model that can test
    whether the language spoken impacts the PR of this specific movie.
    Use an appropriate hypothesis test to test whether the language.
    What would you advise the movie studio regarding the language to be
    spoken? \textbf{[6 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```
=======
---
title: "QRM II Graded Assignment (13)"
subtitle: "Period 1, 2026"
author: "Fill in your group number and names here"
date:  "`r format(Sys.Date(), '%d-%m-%Y')`"
output:
  pdf_document:
    number_sections: true
  html_document:
    df_print: paged

header-includes:
- "\\setcounter{section}{-1}"
- |
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{
    showspaces = false,
    showtabs = false,
    breaklines,
    commandchars=\\\{\}
format:
  html:
    code-overflow: wrap
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This assignment is to be completed in groups of 4-5. Further, all
students in your group need to be assigned to the same R tutorial group
(Friday's tutorial). You can sign yourself up for a group on Canvas.
Please do so
\textbf{before the start of your first R tutorial on Friday September 4th.}
You can use the Discussion Board in Canvas if you do not have a group
yet or if your group is incomplete.

The assignment has 5 parts, and each part corresponds to the course
material of that week (with the exclusion of week 6, for which there is
no R programming material).

You are supposed to hand in these assignments on Canvas at the following
dates:

- **Deadline 1** *Sunday September 27th, at 23:59pm*: you are supposed
  to hand in weeks 1, 2, and 3 of this assignment. This will determine
  18% of your overall course grade
- **Deadline 2** *Sunday October 11th, at 23:59pm*: you are supposed to
  hand in weeks 4, and 5 of this assignment. This will determine 12% of
  your overall course grade

The R tutorials (each Friday) will consist of two halves. During the
first half, you will discuss the tutorial exercises. These can be
downloaded separately from Canvas. During the second half, you can work
on this graded assignment within your own group. The purpose is that you
find out how to work with R for doing statistical analyses by yourself.
The tutorial exercises are meant to teach you basic commands to get you
started, but to answer the problem sets in this assignment, you might
need to research your own solutions, and use functions and commands not
described in the tutorial exercises. Learning how to solve your own
research problems is integral part of learning R. When you and your
group get stuck on how to approach an exercise, the hierarchy in finding
your way is as follows:

- use the concepts from the tutorial exercises;
- use the cheat sheets available on Canvas;
- use Google, YouTube, StackOverflow, or another website;
- ask the teacher.

The use of generative AI is \textbf{not} permitted and may result in a
grade of 0. See the AI protocol in the course manual for details.

To answer the assignment, you can simply fill out this R markdown
document. There are designated places which you can fill with R code.
There are also designated spaces for you to answer each question. Often,
the structure of an answer will be as follows. First, you type the R
code in the designated box. This will show how you analyzed the data to
get the answer to the question. Below the box for the R code, you will
then summarize your answer to the question, i.e. what are the
conclusions that you draw from the data analysis?

When handing in, you are supposed to submit this .Rmd file, and a
knitted version of this document. You can knit this document to pdf,
word, or html. Knitting to pdf requires you to have a .tex distribution
installed on your computer. Knitting to Word requires you to have Word
installed.

The exercises are designed such that you should be able to finish the
majority of them during the tutorial each week. If you are not able to
finish them fully during that time, you are expected to work on it in
your own time using the computers on campus or your own device. It is
best to meet as a group in-person when working together. If you want to
work remotely, github is a good platform to guarantee smooth
collaboration. Alternatively, you can email this .Rmd file back and
forth to one another as a group, but this is not recommended as it is
more cumbersome.

We encourage you to keep your code blocks, printing statements, and
final answers, as short as possible. In any case, there is a page limit
of 6 pages per week, which encompasses the total length of this document
which consists of the questions, your coding lines, and your answers.
When your answers to questions of the respective week exceed this page
limit, they will not be graded, resulting in zero points.

Each week consists of 1, 2, or 3 subquestions. The total amount of
points you can earn per week is 20 points.

# Week 1

1.  Find the dataset “movies1.tsv” on Canvas. Describe your data set:
    How many observations does it have. How many variables are there?
    How many subjects? What consists of a subject? \textbf{[4 points]}

```{r}
#observations
NROW(movies1)*NCOL(movies1)
#variables
NROW(movies1)
#subjects
NCOL(movies1)

```

all data acquired from a singular entry/instance during the study is
what consists of a subject

Write your response here.

2.  Which of the following types of variables are present in your data
    set? (i) nominal; (ii) ordinal; (iii); interval; (iv) ratio. If
    present, name one example of such a variable present in your data
    set. \textbf{[4 points]}

```{r}
names(movies1)
```

**nominal** present, an example of this is the "title" variable

**ordinal** present, an example of this is the "vote_average" variable

**interval** present, an example of this is the "release_date" variable

**ratio** present, an example of this is the "budget" variable\`

3.  A movie studio wants to know which types of movies are best at
    generating profit. The measure they use for this is the
    profitability ratio, which is defined as
    $$PR=\frac{Revenue}{Budget}.$$ Perform the following steps to
    provide the movie studio with an analysis which corresponds to their
    request:

<!-- -->

a.  Create the variable PR as the revenue of a movie divided by its
    budget. Report its mean, median, maximum, and minimum.
    \textbf{[2 points]}
b.  As you can probably see from your answer in a.), some movies have a
    PR of "Inf". What does this mean? Why are some movies assigned this
    value? \textbf{[2 points]}
c.  As you can probably see from your answer in a.), some movies have a
    PR of "NA". What does this mean? Why are some movies assigned this
    value? \textbf{[2 points]}
d.  For the movies that have a PR of "Inf", set its PR to "NA". After
    doing this, report the mean, median, maximum, and minimum of PR. How
    do you interpret the mean? \textbf{[2 points]}
e.  What does a PR of at least one mean? What is the fraction of movies
    that have a PR of at least one? \textbf{[2 points]}
f.  Create a boxplot of the variable PR. Make sure it has an appropriate
    title, and appropriate titles and labels for the x- and y-axis.
    Describe the shape of the boxplot. Give $Q_1$, $Q_2$, $Q_3$ and
    $Q_4$. What does this tell you about the nature of making money in
    the movies industry? \textbf{[2 points]}

For each step, you should provide first all the code you used to answer
the question and then formulate an answer using full sentences.

*Step a*

```{r}
movies1$PR <- movies1$revenue / movies1$budget
summary(movies1$PR)

```

**Your Answer:**

mean = infinite median = 2.0409 minimum = 0.0000 maximum = infinite

*Step b*

```{r}
is.infinite(movies1$PR)
```

**Your Answer:**

the reason why some results show a PR of infinite is because they made a
revenue with a budget of \$0.

*Step c*

```{r}

is.na(movies1$PR)

```

**Your Answer:**

the reason why PR is sometimes NA is because the movie didn't make any
revenue, causing the code to divide by 0.

*Step d*

```{r}
movies1$PR[is.infinite(movies1$PR)] <- NA

summary(movies1$PR)

```

**Your Answer:**

the mean here can be interpreted as the mean excluding any results where
PR was either infinite or NA.

*Step e*

```{r}
movies1$PR[is.na(movies1$PR)] <- 0 #to exclude from being greater than 1
countPR1 <- 0
for (PR in movies1) {
  countPR1 <- countPR1 + 1
} 
PR_fraction <- countPR1 / nrow(movies1)
  print(PR_fraction)

```

**Your Answer:**

using the code, we can determine that 3,96% of the dataset results in an
NA.

*Step f*

```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)

boxplot(movies1$PR,
        main = "Boxplot of Profitability Ratio (PR)",
        xlab = "Movies",
        ylab = "Profitability Ratio (PR)")

quantile(movies1$PR, probs = c(0.25, 0.50, 0.75, 1), na.rm = TRUE)

```

**Your Answer:** q_1 = 0.6239106 q_2 = 1.9412588 q_3 = 3.6700769 q_4 =
426.6441000

there are 2 main observations that can be made from looking at these
numbers. first off, the second quarter being greater than 1 shows that
at least 50% of movies earn more revenue than they have to spend on
their budget. secondly, the result of the 4th quarter is a lot higher
than the other results. by looking at the boxplot we can see that this
is the result of an outlier.

# Week 2

1 Is your dataset movies1.tsv the full population, or is it a sample of
a larger population? If the latter, how would you describe the full
population? \textbf{[4 points]}

**Your Answer**

the dataset movies1.tsv is not the full population, but rather a sample
of a larger population. this full population can be described as all
movies ever made, of which the dataset is only a small sample (505).

2 Let M be the event that a movie director is male. Let R be the runtime
of the movie.

a.  Using your data, calculate $P(M)$. What is $P(M')$?. Calculate
    $P(M')$ as well. \textbf{[1 point]}
b.  Assume R is normally distributed with $\mu=107$ and $\sigma=22$,
    calculate $P(90 \leq R \leq 120)$. \textbf{[1 point]}
c.  Calculate $P(90 \leq R \leq 120)$ empirically using your data. How
    accurate were the assumptions about the distribution of R in 2b?
    Which of the assumptions do you consider the most suspect? Explain.
    \textbf{[2 points]}
d.  Using your data, calculate $P(120 \leq R | M')$ \textbf{[2 points]}

*step a*

```{r}


```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

3 For this question, you will again use the profitability ratio PR. Make
sure that PR is defined the same way as in question 3d of week 1. For
this question, you will assume that your data set is the full
population.

a.  What is the mean of the variable PR in your data set?
    \textbf{[2 points]}
b.  Create a new data set, called movies_sample. Make sure that it is a
    random sample of your data set of 25 movies. What is the mean of PR
    in this random sample? How does it compare to the mean of PR in 3a?
    \textbf{[2 points]}
c.  In a for loop, create 100 different samples of 25 movies, as in b,
    and estimate the mean within each sample. Save the mean of each
    sample in a vector called sample_means. So the first position of the
    vector would have the mean of the first sample, the second position
    the mean of the second sample, etc. Print this vector.
    \textbf{[2 points]}
d.  Summarize and make a histogram of sample_means. What is the mean,
    standard deviation and shape of its distribution?
    \textbf{[2 points]}
e.  Using the formulas of the *Central Limit Theorem*, give the
    distribution of the sample mean of PR in a sample of 25 movies from
    you population (including its expected value and standard
    deviation). How do these values compare to your answers at d.)?
    \textbf{[2 points]}

*step a*

```{r}
mean(movies1$PR)

```

**Your Answer:**

the mean of the variable PR is 3.445837. this indicates that the average revenue was over 3x its budget.

*step b*

```{r}
movies_sample <- movies1[sample(nrow(movies1), 25), ]

mean(movies_sample$PR)

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
sample_means <- numeric(100)

for (i in 1:100) {
  movies_sample <- movies1[sample(nrow(movies1), 25), ]
  sample_means[i] <- mean(movies_sample$PR)
}

head(sample_means)

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
summary(sample_means)

mean(sample_means)

sd(sample_means)

hist(sample_means,
     main = "Distribution of Sample Means",
     xlab = "Sample Mean of PR")


```

**Your Answer:**

Write your formulated response here.

*step e*

**Your Answer:**

Write your formulated response here.

# Week 3

1.  For the next part of the assignment, assume that the movies in your
    data frame are a random sample of a larger population of movies.

<!-- -->

a.  Create a new data set that only includes movies that are of the
    genre "Thriller". For these thriller movies, give a 99 percent
    confidence interval for the variable *vote_average*.
    \textbf{[2 points]}

b.  According to IMDB, the average movie is rated with a 6.5. Using your
    data, test for the null hypothesis that thriller movies are at least
    as good as the average movie, against the alternative hypothesis
    that thriller movies are rated worse than the average movie. Test
    this hypothesis using an approporiate five-step procedure. What is
    your p-value and what do you conclude? \textbf{[2 points]}

*step a*

```{r}
movies1 <- read.delim("movies1.tsv")

thriller <- subset(movies, genre == "Thriller")

t.test(thriller$vote_average, conf.level = 0.99)

```

**Your Answer:**

we are 99% confident that the true mean vote average of thriller movies
in the population lies between [5.644845, 6.299771] *step b*

```{r}
#WRITE YOUR CODE HERE
t.test(thriller$vote_average,
       mu = 6.5,
       alternative = "less")

```

**Your Answer:**

five step procedure 1. hypothesis H₀: μ ≥ 6.5 the average rating of
thriller movies is at least 6.5

H₁: μ \< 6.5 the average rating of thriller movies is lower than 6.5

2.  significance level we use α = 0.05

3.  test statistic you can see the code above. with t = -4.2782 and df =
    64

4.  determine the p-value p-value = 0.0000321 0.0000321 \< 0,05, we
    reject H₀

5.  conclusion we reject the null hypothesis and conclude that there is
    sufficient evedence to state that the average rating of thriller
    movies is lower than a 6.5. the mean is given by point 3 and shows a
    mean of 5.9723, which is also below 6.5

2

a.  How many movies in your sample had a female lead actor? How many had
    a male lead actor? \textbf{[2 points]}
b.  Test the null hypothesis that for any given movie the chance that
    the lead actor is male or female is equal. Clearly state your null
    hypothesis and alternative hypothesis, and your chosen significance
    level. Use an appropriate R function to test your hypothesis, and
    state your conclusion. Also give the p-value that corresponds to
    your test statistic. \textbf{[2 points]}
c.  What is the variance of the profitability ratio (PR) for movies with
    a male lead actor? What is the variance of profitability ratio for
    movies with a female lead actor? Make sure that PR is defined in the
    same way as in week 1. \textbf{[2 points]}
d.  Assume that the variance of PR for movies with a male lead actor in
    your data is the same as the variance for movies with a male lead
    actor in your population (that is, there is no sampling uncertainty
    in this estimate). Now, set up a hypothesis test to test for the
    null hypothesis that the PR for movies with a female lead is equal
    to the variance for movies with a male lead actor. Clearly state
    your null hypothesis and alternative hypothesis, and your chosen
    significance level. Calculate your test statistic and tell how your
    test statistic is distributed, and state your conclusion. Also give
    the p-value that corresponds to your test statistic.
    \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE
table(movies1$first_actor_gender)

```

**Your Answer:**

There are 130 female lead actors and 352 male lead actors

*step b*

```{r}
binom.test(
  sum(movies1$first_actor_gender == "male", na.rm = TRUE),
  sum(!is.na(movies1$first_actor_gender)),
  p = 0.5
)

```

**Your Answer:**

1.  hypothesis H₀:pmale=pfemale=0.5 The probability of a male lead actor
    equals the probability of a female lead actor H₁:pmale ≠ pfemale it
    is not equal to eachother

2.  significance level we use α = 0.05

3.  R function see the code above

There were 352 male first actors out of 482 movies, giving a sample
proportion of 73.03%. The p-value is 2.2 × 10⁻¹⁶, which is smaller than
0.05.

Therefore, we can reject the null hypothesis. There is significant
evidence that the probability of a male first actor is different from
50%. In this sample, the proportion of male first actors is
approximately 73%.

*step c*

```{r}
male <- subset(movies1, first_actor_gender == "male")
female <- subset(movies1, first_actor_gender == "female")
var(male$PR, na.rm = TRUE)
var(female$PR, na.rm = TRUE)

```

**Your Answer:**

variance of PR for movies with a male lead: 77.73981 Variance of PR for
movies with a female lead: 1398.035

*step d*

```{r}
n_female <- sum(!is.na(female$PR))
test_stat <- (n_female - 1) * var_female / var_male

test_stat

df <- n_female - 1

p_value <- 2 * min(
  pchisq(test_stat, df = df),
  1 - pchisq(test_stat, df = df)
)

p_value

```

**Your Answer:**

1.  hypothesis H₀:σ\^2 male= σ\^2 female=0.5 The variance of PR for
    female lead movies equals the variance for male lead movies of a
    female lead actor H₁:σ\^2 male ≠ σ\^2 female the variance is
    different

2.  significance level we use α = 0.05

3.  R function see the code above because the male variance is known, we
    use a chi-squared test

4.  p-value see the code above. The P-value is 0

5.  conclusion The p-value is \<0.05, this means we reject H₀ and the is
    sufficient evidence to conclude that the variance of the probability
    ratio for movies with a female lead actor differs from the movie
    with male lead actors

3

a.  Create a new variable called genre2. Make sure that the three most
    popular genres remain the same, but that all the other genres get
    categorized into one genre called "Other". Report a frequency table
    of this new variable genre2. \textbf{[2 points]}
b.  Create a scatter plot with each type of genre2 on the x axis and the
    mean of PR within that genre on the y-axis. Make sure it has an
    appropriate title, and appropriate titles and labels for the x- and
    y-axis. Which movie genre has the highest PR? Which has the lowest?
    \textbf{[2 points]}
c.  Recreate the scatter plot, but now add bars around each point,
    indicating the 95% confidence interval. \textbf{[2 points]}
d.  Now, create a new data frame which is a random subsample of n=100 of
    your full data frame. Recreate the plot in c.) How do the confidence
    intervals compare to the confidence intervals you plotted in c.)?
    \textbf{[2 points]}

*step a*

```{r}
table(movies1$genre)


movies1$genre2 <- ifelse(movies1$genre %in% c("Drama", "Comedy", "Thriller"),
                         movies1$genre, "Other")

table(movies1$genre2, useNA = "no")

```

**Your Answer:**

The three most popular genres are Drama, comedy and thriller

*step b*

```{r}
aggregate(PR ~ genre2, data = movies1, mean, na.rm = TRUE)

genre_means <- aggregate(PR ~ genre2, data = movies1, mean, na.rm = TRUE)

plot(as.factor(genre_means$genre2),
     genre_means$PR,
     main = "Mean PR by Movie Genre",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

```

**Your Answer:**

the movie genre with the highest PR are the thriller movies with a PR of
8.921 and the movie genre with the lowest PR are the Drama movies with a
PR of 1.997

*step c*

```{r}
genres <- unique(na.omit(movies1$genre2))

means <- numeric(length(genres))
lower <- numeric(length(genres))
upper <- numeric(length(genres))

for (i in 1:length(genres)) {
  x <- movies1$PR[movies1$genre2 == genres[i]]
  x <- x[!is.na(x)]
  
  test <- t.test(x)
  
  means[i] <- mean(x)
  lower[i] <- test$conf.int[1]
  upper[i] <- test$conf.int[2]
}

x <- 1:length(genres)

plot(x, means,
     xaxt = "n",
     main = "Mean PR by Movie Genre with 95% Confidence Intervals",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

axis(1, at = x, labels = genres)

arrows(x, lower,
       x, upper,
       angle = 90,
       code = 3,
       length = 0.05)


```

**Your Answer:**

see the code above

*step d*

```{r}
set.seed(123)

movies_sample <- movies1[sample(nrow(movies1), 100), ]
genres <- unique(na.omit(movies_sample$genre2))

means <- numeric(length(genres))
lower <- numeric(length(genres))
upper <- numeric(length(genres))

for (i in 1:length(genres)) {
  x <- movies_sample$PR[movies_sample$genre2 == genres[i]]
  x <- x[!is.na(x)]
  
  test <- t.test(x)
  
  means[i] <- mean(x)
  lower[i] <- test$conf.int[1]
  upper[i] <- test$conf.int[2]
}

x <- 1:length(genres)

plot(x, means,
     xaxt = "n",
     main = "Mean PR by Movie Genre (Sample of 100)",
     xlab = "Movie Genre",
     ylab = "Mean PR",
     pch = 19)

axis(1, at = x, labels = genres)

arrows(x, lower,
       x, upper,
       angle = 90,
       code = 3,
       length = 0.05)
```

**Your Answer:**

the confidence intervals are generally wider for the random sample of
100 observations. this is because the smaller sample size results in a
larger standard error and therefore uncertainty around the estimated
mean

# Week 4

1.  There is an argument going on in the movie studio. *Bob* claims that
    production budgets are getting out of hand, and that the studio
    should focus on making cheaper movies. *Chantal* disagrees. She
    tells Bob that \`\`The profitability ratio of the movie will remain
    similar, no matter how much the budget is''.

<!-- -->

a.  Set up a regression model to test Chantal's claim, and estimate it.
    That is, estimate:
    $$\text{PR}_i=\beta_0+\beta_1 \text{Budget}_i +\varepsilon_i.$$
    Print a summary of your estimated model. \textbf{[2 points]}
b.  What is the estimated value of $\beta_1$ how do you interpet it?
    \textbf{[2 points]}
c.  Test for the null hypothesis that $\beta_1 = 0$. Report the p-value
    and state your conclusion. \textbf{[2 points]}
d.  Who do you think is correct? Bob or Chantal? What would you advise
    the movie studio to do? \textbf{[2 points]}
e.  Make a histogram of the residuals of your model. Based on the
    histogram, do you have any reason to doubt the validity of your
    model? Explain. \textbf{[2 points]}
f.  Estimate hatvalues for each observation that you used to estimate
    your model. Do any hatvalues exceed the critical value? Based on
    this analysis, do you hvae any reason to doubt the validity of your
    model? \textbf{[2 points]}
g.  Based on your analysis in f.), estimate your model again, but remove
    any outliers. Print a summary of your model and again test for the
    null hypothesis that $\beta_1 = 0$. What do you conclude? Based on
    this new model, would your advice to the movie studio in question d.
    change? \textbf{[2 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step f*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step g*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

2.  

<!-- -->

a.  Make a scatterplot with vote_average on the y-axis, and runtime on
    the x-axis. Within the same scatterplot, draw a straight line which
    summarizes the association between the average vote and the runtime.
    \textbf{[3 points]}
b.  Using the insights from the scatterplot, your linear model, and your
    data, find an example of a movie that vastly overperformed. That
    means, find a movie that had much higher average vote than expected,
    given its runtime. For this movie, report its vote_average, its
    predicted vote_average, and its residual. \textbf{[3 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

# Week 5

a.  Create a plot of the mean PR by year of release. Include 95%
    confidence intervals around each mean Do you see any indication of a
    time trend in the PR? \textbf{[4 points]}
b.  Estimate an OLS model which has as dependent variable the PR of a
    movie, and as independent variable the log of budget, a dummy for
    each level that genre2 can take, and the year of release. Show a
    summary of the resulting model and interpret each coefficient.
    \textbf{[4 points]}

The movie studio that you work is releasing a new movie in May of 2026.
It will be a Comedy movie with a budget of 40,000,0000. It will have a
runtime of 160 minutes.

c.  Estimate a model that is able to predict the revenue of this movie.
    Give its predicted revenue and include a 95% prediction interval.
    \textbf{[6 points]}
d.  Plot the residuals against various independent variables in the
    model. Do you find any evidence of heteroskedasticity?
    \textbf{[2 points]}
e.  The movie is set in Germany. The director wants to make the movie
    with only german-speaking actors. The executive producer is strongly
    against this, as she is afraid that movies that are not english
    spoken will have a low profit ratio. Estimate a model that can test
    whether the language spoken impacts the PR of this specific movie.
    Use an appropriate hypothesis test to test whether the language.
    What would you advise the movie studio regarding the language to be
    spoken? \textbf{[6 points]}

*step a*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step b*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step c*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step d*

```{r}
#WRITE YOUR CODE HERE

```

**Your Answer:**

Write your formulated response here.

*step e*

```{r}
#WRITE YOUR CODE HERE

```
>>>>>>> 7531e3d6c454d2fc7a948a38da97779fab8a5c00
